\begin{ingrid}
(iri.columbia.edu/terms/s2s/1)cvn datadownloadsareRestricted
/Cookie varies_on
continuedataset:

/description (WWRP/WCRP Sub-seasonal to Seasonal Prediction Project) def

link:
/name (ECMWF) def
/description (ECMWF S2S Wiki Page) def
/href (https://software.ecmwf.int/wiki/display/S2S) def
:link

link:
/name (Model_Table) def
/description (S2S Model Description Table at ECMWF S2S Wiki Page) def
/href (https://software.ecmwf.int/wiki/display/S2S/Models) def
:link

link:
/name (S2S_Project) def
/description (WWRP/WCRP S2S Project Page) def
/href (http://wwww.s2sprediction.net/) def
:link

link:
/name (README) def
%/description (Notes on the S2S Database in the IRI Data Library) def
/description (Please see these notes for explanation on accessing and using the S2S Database in the IRI Data Library) def
/href (https://www.dropbox.com/s/gd4eou1l3vn90d0/S2S_IRIDL_notes.pdf?dl=0) def
:link

link:
/name (BAMS_paper) def
/description (The Subseasonal to Seasonal (S2S) Prediction Project Database) def
/href (http://journals.ametsoc.org/doi/abs/10.1175/BAMS-D-16-0017.1) def
:link

link:
/name (Wiki) def
/description (IRI Wiki Page with IRIDL S2S data examples) def
/href (http://wiki.iri.columbia.edu/index.php?n=Climate.S2S-IRIDL) def
:link

link:
/name (S2S Model Updates) def
/description (News Updates on S2S Model Changes from the ECMWF S2S Archive) def
/href (https://confluence.ecmwf.int/display/S2S/News) def
:link

/reference (Vitart, F., C. Ardilouze, A. Bonet, A. Brookshaw, M. Chen, C. Codorean, M. Déqué, L. Ferranti, E. Fucile, M. Fuentes, H. Hendon, J. Hodgson, H. Kang, A. Kumar, H. Lin, G. Liu, X. Liu, P. Malguzzi, I. Mallas, M. Manoussakis, D. Mastrangelo, C. MacLachlan, P. McLean, A. Minami, R. Mladek, T. Nakazawa, S. Najm, Y. Nie, M. Rixen, A.W. Robertson, P. Ruti, C. Sun, Y. Takaya, M. Tolstykh, F. Venuti, D. Waliser, S. Woolnough, T. Wu, D. Won, H. Xiao, R. Zaripov, and L. Zhang, 2017: The Subseasonal to Seasonal (S2S) Prediction Project Database. Bull. Amer. Meteor. Soc., 98, 163–173, https://doi.org/10.1175/BAMS-D-16-0017.1) def

/license (Acknowledgement:  Please add the following Acknowledgement to any publication resulting from the use of the S2S database: “This work is based on S2S data. S2S is a joint initiative of the World Weather Research Programme (WWRP) and the World Climate Research Programme (WCRP). The original S2S database is hosted at ECMWF as an extension of the TIGGE database”. For dataset source, please cite: Vitart et al., The Sub-seasonal to Seasonal (S2S) Prediction Project Database. Bull. Amer. Meteor. Soc., 98(1), 163-176. doi: http://dx.doi.org/10.1175/BAMS-D-16-0017.1.  Besides the above acknowledgement, users should register any journal articles (or other scientific documents) that are based on S2S data by sending an email to: Subseasonal_to_Seasonal_Prediction@googlegroups.com.) def

% See instructions for creating variable definitions from S2S GRIB2 files in the BOM/forecast/control/index.tex file

:dataset
\end{ingrid}
