\begin{ingrid}
continuedataset:
/IRIONLY datadownloadsareIRIonlyPassword
/long_name (Asian precipitation from APHRODITE) def
/description (Asian precipitation products created by the Research Institute for Humanity and Nature and Meteorological Research Institute of Japan Meteorological Agency) def
link: 
/name (APHRODITE's Water Resources Website) def
/href (http://aphrodite.st.hirosaki-u.ac.jp/) def
/description (the original source of this dataset) def
:link

/iridl:hasSemantics [(iridlsemantics:APHRODITE)(iridlsemantics:RIHN)(iridl:MRI)] def
/references (Hamada2011 Xie_etal2007 Yatagai_etal2009 Yatagai_etal2012) def
:dataset
\end{ingrid}

Hamada, A., O. Arakawa and A. Yatagai, 2011: An automated quality control method for daily rain-gauge data. Global Environmental Research, V15N2, pp183-192.

Xie, P., A. Yatagai, M. Chen, T. Hayasaka, Y. Fukushima, C. Liu, and S. Yang (2007). A gauge-based
analysis of daily precipitation over East Asia, Journal of Hydrometeorology, 8, 607-627.

Yatagai, A. O. Arakawa, K. Kamiguchi, H. Kawamoto, M. I. Nodzu and A. Hamada (2009): A 44-year daily
gridded precipitation dataset for Asia based on a dense network of rain gauges, SOLA, 5, 137-140,
doi:10.2151/sola.2009-035.

Yatagai, A., K. Kamiguchi, O. Arakawa, A. Hamada, N. Yasutomi and A. Kitoh (2012): APHRODITE:
Constructing a Long-term Daily Gridded Precipitation Dataset for Asia based on a Dense Network of
Rain Gauges, Bull. Amer. Meteor. Soc., 93, 1401-1415.
doi: http://dx.doi.org/10.1175/BAMS-D-11-00122.1

