\begin{ingrid}
continuedataset:
/name (ensemble15)def
 /description (Forecasts initialized with NCEP early CDAS) def
 /history (Created Wed Apr 25 08:06:23 2007 UTC) def
 /title (NCEP/CDC MRF Reforecast Data) def
 /Conventions (COARDS) def
 /platform (none) def
grid:
/name (X)def
/units (degree_east)def
 0.0 2.5 357.5
:grid
grid:
/name (Y)def
/units (degree_north)def
 90. 2.5 -90.
:grid
grid:
/name (lag)def
/units (hours) def
12. 12. 360.
%/units (hours since 1-1-1 00:00:0.0)def
% 17587020. 12. 17587368.
:grid
grid:
/name (members)def
/units (unitless)def
 1. 1. 15.
:grid

grid:
/name /S def
/units (days since 2007-08-24 00:00:00) def
/long_name (Forecast Start Time) def
/standard_name (forecast_reference_time) def
/defaultvalue { last } def
/pointwidth 0 def
01 Jan 2000 julian_day
24 Aug 2007 julian_day sub
%0
1
%20 Jan 2008 julian_day
30 May 2013 julian_day % systemtime (%d %b %Y) 12 strftime interp julian_day
24 Aug 2007 julian_day sub
%01 Jan 2007 julian_day sub
:grid

%S {S /unixtime unitconvertbyattribute exch scale_factor mul add_offset add (/Data/data21/noaa/esrl/psd/refcst/apcp.refcst_ens.grid.%m%d00.%Y.nc) 100 strftime nip}
%removeextrausing

%/expires last 1 add 2007 08 24 ymd2rjt add rjt2ymd ymd2systemtime 6 3600 mul add  def
%name exch def
%/expires S .expires def
/last_modified S .last_modified def
 /apcp{
[ X Y lag | members S] (/Data/data21/noaa/esrl/psd/refcst/apcp.refcst_ens.grid.%m%d00.%Y[S].nc) [S] readdatafile:
/name (apcp) def
 /var_desc (Accumulated precipitation) def
 /parent_stat (Mean) def
 /long_name (Accumulated precipitation) def
 /precision -999. def
 /units /mm def
 /valid_range [ -9.96920997E36 9.96920997E36 ] def
 /statistic (Mean) def
 /actual_range [ 0.0 133.22099 ] def
 /Dataset (NCEP/CDC MRF Reforecast) def
 /missing_value 32766 def
 /scale_factor 0.01 def
 /add_offset 327.64999 def
 /shortarraytype netcdfrecords :readdatafile
}defasvarsilent
 /ensemble_member{
[ members | S] (/Data/data21/noaa/esrl/psd/refcst/apcp.refcst_ens.grid.%m%d00.%Y[S].nc) [S] readdatafile:
/name (ensemble_member) def
 /long_name (ensemble member (0 is control, +1 is p1, -1 is n1, etc)) def
 /units /unitless def
 /shortarraytype netcdfrecords :readdatafile
}defasvarsilent


:dataset
\end{ingrid}
