\begin{ingrid}
continuedataset:
datasetdefs:
/fileavail {
prec dataflag[X Y]average 0 maskle 0 flaggt L first VALUE M first VALUE grid: /name /S1 def /units monthtimename def /gridtype periodic def Jan 1 Dec :grid grid: /name /S2 def /units monthtimename def /pointwidth 12 def 1 Jul 1981 ensotime 12 1 Jul 2012 ensotime :grid add 6.5 sub S .first S .last masknotrange /pointwidth 0 def[S]sample-along /fullname (fileavail) def
} defasvar
:datasetdefs
 /Conventions (CF-1.0) def
 /history (FERRET V6.401   11-Jul-11) def
 /references (Kirtman_etal2014) def
\end{ingrid}
grid:
/name (LON)def
/units (degree_east)def
 0.0 1. 359.
:grid
grid:
/name (LAT)def
/units (degree_north)def
 -90. 1. 90.
:grid
grid:
/name (TIME)def
/units (days since 1982-08-01 00:00:00)def
values: 15.5 46. 76.5 107. 137.5 168.5 198. 227.5 258. 288.5 319. 349.5 :values
:grid
\begin{ingrid}
link:
/name (data_availability) def
/href (fileavail/mark/exch/S2/exch[S1]table:/mark/:table/.html) def 
:link
grid:
/name (X)def
/units (degree_east)def
 0.0 1. 359.
/standard_name (longitude) def
:grid
grid:
/name (Y)def
/units (degree_north)def
 -90. 1. 90.
/standard_name (latitude) def
:grid
grid:
/name (S)def
/long_name (Forecast Start Time) def
/units (months since 1960-01-01)def
/calendar /360 def
/standard_name (forecast_reference_time) def
/pointwidth 0 def
1        Jan 1982 ensotime
        1.
1          Feb 2012 ensotime
:grid
grid:
/name (L) def
/long_name (Lead) def
/units (months) def
/standard_name (forecast_period) def
0.5 1 11.5
:grid
/M 10 NewIntegerGRID
/long_name (Ensemble Member) def
/standard_name (realization) def
 name exch def
/T { S L add
/long_name (Time) def
/standard_name (time) def } defasvarsilent
grid:
/name (Z) def
/units (m) def
/long_name (Height) def
/standard_name (height) def
2 :grid
 /prec{
[ X Y | M L S] (/data/dstore4/iri/modelling/daved/NMME_Data.D/GFDL_CM2.1.D/%b.D/%Y%m[S]01.1x1.precip_ens%2.2d[M].nc) [ M S] readdatafile:
/name (PRECIP_1X1) def
 /units /unitless def
 /missing_value -9.99999979E33 def
 /long_name (PRECIP[GX=VAR_1X1[D=1],GY=VAR_1X1[D=1]]) def
/long_name (Total Precipitation) def
/standard_name (lwe_precipitation_rate) def
 /history (From atmos_ens01.198208-201107.precip) def
 /realarraytype netcdfrecords :readdatafile
86400 mul
/units (mm/day) def
}defasvarcachesilent
/sst{
[ X Y /Z0 1 NewIntegerGRID /netcdfgrid true def | M L S] (/data/dstore4/iri/modelling/daved/NMME_Data.D/GFDL_CM2.1.D/%b.D/%Y%m[S]01.1x1.sst_ens%2.2d[M].nc) [ M S] readdatafile:
/name (SST_1X1) def
 /units /Celsius_scale def
 /missing_value -9.99999979E33 def
 /long_name (TEMP[GX=VAR_1X1[D=1],GY=VAR_1X1[D=1],K=1]) def
/long_name (Sea Surface Temperature) def
/standard_name (sea_surface_temperature) def
 /history (From 1982-2010.temp_month_ens01) def
 /realarraytype netcdfrecords :readdatafile
Z0 removeGRID
CopyStream
}defasvarcachesilent
/tref{
[ X Y | Z M L S] (/data/dstore4/iri/modelling/daved/NMME_Data.D/GFDL_CM2.1.D/%b.D/%Y%m[S]01.1x1.t_ref_ens%2.2d[M].nc) [ M S] readdatafile:
/name (T_REF_1X1) def
 /units /Kelvin_scale def
 /missing_value -9.99999979E33 def
 /long_name (T_REF[GX=VAR_1X1[D=1],GY=VAR_1X1[D=1]]) def
/long_name (Reference Temperature) def
/standard_name (air_temperature) def
 /history (From atmos_ens01.198208-201107.t_ref) def
 /realarraytype netcdfrecords :readdatafile
}defasvarcachesilent
:dataset
\end{ingrid}
