Benno,

 I just had a gridded d18Oseawater dataset published. It falls out of Gavin Schmidt's d18Oseawater & salinity database. It is hosted on the GISS website, but Peter deMenocal suggested adding it ingrid, as well.

Gridded Dataset: http://data.giss.nasa.gov/o18data/grid.html   (1x1x33 levels on the WOA01 grid)
Reference:  LeGrande, A.N., and G.A. Schmidt 2006. Global gridded data set of the oxygen isotopic composition in seawater. Geophys. Res. Lett. *33*, L12604, doi:10.1029/2006GL026011.
http://pubs.giss.nasa.gov/abstracts/2006/LeGrande_Schmidt.html
Fortran Binary format (this is what it was created in: 33 records, each record: character*80,real*4(360,180).)
NetCDF format
If it would be easier for you, I can sftp the data to you or make it available.

Database: http://data.giss.nasa.gov/o18data/
Reference: Schmidt, G.A., G. R. Bigg and E. J. Rohling. 1999. "Global Seawater Oxygen-18 Database". http://data.giss.nasa.gov/o18data/ls -
ASCII format

Allegra 
\begin{ingrid}
continuedataset:
datasetdefs:
/d18o { v1p0 .d18o } def
:datasetdefs
/v1p0 {
(/Data/data7/nasa/giss/LeGrande_Schmidt2006/calculated_d18O.nc) readfile
/long_name (v1.0) def
link:
/name (v1.1) def
/href (http://iridl.ldeo.columbia.edu/SOURCES/.NASA/.GISS/.LeGrande_Schmidt2006/.v1p1/) def
/description (LeGrande and Schmidt 2006 Version 1.1) def
/semantics /dcterm:isReplacedBy def
:link
d18o
/iridl:hasSemantics (iridl:dO18) def
name exch def
}
defasvarsilent
/v1p1 {
(/Data/data7/nasa/giss/LeGrande_Schmidt2006/calculated_d18O_v1_1.nc) readfile
/long_name (v1.1) def
d18o
/iridl:hasSemantics (iridl:dO18) def
name exch def
}
defasvarsilent
/description (Global gridded dataset of the oxygen isotopic composition in seawater) def
link:
/name (VSMOW) def
/href (http://en.wikipedia.org/wiki/VSMOW) def
:link
/references (LeGrande_Schmidt2006) def
/iridl:hasSemantics (iridl:GISS) def
:dataset
\end{ingrid}
