Benno - see response from ECMWF below.   Seems
like IRIONLY can become LDEOONLY which is
fantastic!  Richard

-- 
Richard Seager
Doherty Senior Research Scientist
Lamont Doherty Earth Observatory
Rt 9W, Palisades, NY 10964
Tel:  845-365-8743
FAX:  845-365-8736
email: rich@maatkare.ldeo.columbia.edu

---------- Forwarded message ----------
Date: Tue, 12 Apr 2005 11:26:24 +0100
From: Data.Services <Data.Services@ecmwf.int>
To: Richard Seager <rich@maatkare.ldgo.columbia.edu>
Cc: Data.Services <Data.Services@ecmwf.int>, Joerg Urban <Joerg.Urban@ecmwf.int>
Subject: Re: access to ERA 40

Dear Richard Seager,

I have discussed this with my management and we are happy for
Lamont Doherty Earth Observatory of Columbia University and IRI
to share ERA-40 data downloaded from the data server.

Regards

Keith Fielding

>
> Dear Sirs and Madams,
>
> I  have signed up to use the ERA-40 Reanalyis in
> our climate research work at the Lamont Doherty Earth
> Observatory of Columbia University and accept the
> conditions.
>
> Our sister institute here, the International Research
> Institute for Climate Prediction (IRI) already has
> the ERA 40 data and serves it through their online
> data library, which we use for all our other data
> and model simulations.  Currently the IRI restricts
> access to ERA 40 to IRI personnel only.
>
> Would it be possible for ECMWF to allow the IRI to
> extend access to the ERA 40 data to our climate research
> group at the Observatory?  This would be, for us, by
> far the easiest way to use the data and would prevent
> unneccessary duplication of data sets in adjacent
> buildings on our campus!
>
> Many thanks,
> Richard Seager
>

-- 
ECMWF Data Services
Email: Data.Services@ecmwf.int
WWW  : http://www.ecmwf.int
Fax:  (0118) 986 9450
Intl: (+44-118) 986 9450 
\begin{ingrid}
continuedataset:
(iri.columbia.edu/perm/ecmwf/1)cvn dataareRestricted
/Cookie varies_on
/description (ECMWF 40-Year Reanalysis) def
/references (Uppala_etal2005) def
:dataset
\end{ingrid}
