Information for the use of the monthly 1-degree SST NMC climatology

This climatology has been derived from monthly optimum interpolation
(OI) SST analyses with an adjusted base period of 1950-79. A complete
paper on the SST climatology has been prepared and sent to the Journal
of Climate.  A copy of the paper can be found in the directory,
climpap, which is on the same level as this directory, aoiclim.  The
paper is contained in 14 UNIX compressed files. To obtain the paper
from this directory:  "cd ..", "cd climpap", ftp the 14 files in binary
mode, uncompress them, and send them to a postscript printer.  An
abstract of the paper is attached to the end of this note.  The paper
should be referenced as:

Reynolds, R. W. and T. M. Smith, 1994: A high resolution global sea
     surface temperature climatology. J. Climate, (submitted).

The monthly climatology fields are stored in the binary file:
aoi.clim. 
\begin{ingrid}
continuedataset:
grid:
/name /X def
degE
periodic
-179.5 1. 179.5
:grid
grid:
/name /Y def
degN
-89.5 1. 89.5
:grid
grid:
/name /T def
/units monthclimoname def
periodic
Jan 1. Dec
:grid
variable:
/name /sst def
/long_name (Sea Surface Temperature) def
/units /Celsius def
/labelinterval 5. def
/scale_factor .01 def
/history (Climatological sea surface temperature (blended from ship and buoy, data (1950-1979)).) def
/iridl:hasSemantics (iridl:climatology) def
/references (Reynolds_Smith1995) def
sstcolorscale
grids: X Y | T :grids
/PLOTCOAST 1 def
file:
i*2
/name (/Data/data1/ocean/nmc/sstoimonthclimo) def
:file
:variable
:dataset
\end{ingrid}
