\begin{ingrid}
continuedataset:

/description (CRU TS4.05: Climatic Research Unit (CRU) Time-Series (TS) Version 4.05 of High Resolution Gridded Data of Month-by-month Variation in Climate (Jan. 1901 - Dec. 2020)) def

 /contact (BADC) def
 /title (CRU TS4.05) def
 /comment (Access to these data is available to any registered CEDA user) def
 /Conventions (CF-1.4) def
 /institution (Data held at British Atmospheric Data Centre, RAL, UK.) def
 /references (Harris_etal2020) def

 /note (Please use the attribution Climatic Research Unit (University of East Anglia) and Met Office) def

 /citation (University of East Anglia Climatic Research Unit; Harris, I.C.; Jones, P.D.; Osborn, T. (2021): CRU TS4.05: Climatic Research Unit (CRU) Time-Series (TS) version 4.05 of high-resolution gridded data of month-by-month variation in climate (Jan. 1901- Dec. 2020). NERC EDS Centre for Environmental Data Analysis, date of citation. https://catalogue.ceda.ac.uk/uuid/c26a65020a5e4b80b20018f148556681) def

link:
/name (BADC Documentation Page) def
/description (CRU TS4.05: Climatic Research Unit (CRU) Time-Series (TS) version 4.05 of high-resolution gridded data of month-by-month variation in climate (Jan. 1901- Dec. 2020)) def
/href (https://catalogue.ceda.ac.uk/uuid/c26a65020a5e4b80b20018f148556681) def
:link

link:
/name (Reference Document) def
/description (Harris et al. (2020) Scientific Data paper) def
/href (https://www.nature.com/articles/s41597-020-0453-3) def
:link

link:
/name (Release Notes) def
/description (Release notes for CRU TS v4.05) def
/href (https://crudata.uea.ac.uk/cru/data/hrg/cru_ts_4.05/Release_Notes_CRU_TS4.05.txt) def
:link

link:
/name (DataSource) def
/description (Data Source) def
/href (https://crudata.uea.ac.uk/cru/data/hrg/cru_ts_4.05/) def
:link

:dataset
\end{ingrid}
