
akhmadfaqih  akhmadfaqih@gmail.com via iri.columbia.edu 
	
Jun 1 (3 days ago)
		
to Andrew, Benno, Rizaldi, Kye

Dear Andy,

Apologize for the delay. I have sent an email to Pak Rizaldi since a few days ago, asking about your questions but never get any reply. Today, I just had a chance to ask him directly about your questions. Here are the answers: 
 1) Naming
 As you indicated, we can use the convention Dataset name: ASEAN Compedium.
 Please spell out the exact names that should be used for each.

 2) Will more data be added later, or will the dataset stay as it is? It will stay as it is.

 3) Please give some details of where the data is originally from. 
 The data was taken from the ASEAN Compedium database.

 4) Is the dataset part of an experiment, or monitoring? I am not sure about this. Pak Rizaldi said that we have the hard copy of the datasets in the laboratory of climatology, so I have to check on this, maybe on Monday. 

 5) Is there a paper/publication that documents it? No, it seems there is no paper/publication about this dataset. However, I have to check the hard copy of the dataset in our lab. Maybe from there we could get specific information about it. Pak Rizaldi said that the data that we used is an updated version of the hardcopy.  
Sorry again for a very long reply from us. Thanks.

Kind regards,
Akhmad Faqih
\begin{ingrid}
/CCROM-ASEAN dataareIRIonlyPassword
(/Data/data5/ipb/ccrom/Obs_Indonesia_ASEANcomp_197501_199912.nc) continuewithCDF
  lon
   /scale_max 141 def
   /scale_min 95 def
   name exch def
  lat
   /scale_min -11 def
   /scale_max 6 def
   name exch def
continuedataset:
:dataset
\end{ingrid}
