\begin{ingrid}
continuedataset:
/description (Time-Invariant Data) def
link:
/name (source) def
/description (original OpenDAP Server) def
/href (http://www.esrl.noaa.gov/psd/thredds/dodsC/Datasets/20thC_ReanV2/catalog.html) def
:link
link:
/name (dataset_documentation) def
/description (Data Set Documentation) def
/href (http://www.esrl.noaa.gov/psd/data/gridded/data.20thC_ReanV2.html) def
:link

/citation (Compo, G.P., J.S. Whitaker, and P.D. Sardeshmukh, 2006: Feasibility of a 100 year reanalysis using only surface pressure data. Bull. Amer. Met. Soc., 87, 175-190.) def
 /platform (Model) def
 /references (Compo_etal2011 Compo_etal2006 Whitaker_etal2004) def
%/references (http://www.esrl.noaa.gov/psd/data/gridded/data.20thC_ReanV2.html) def
 /institution (NOAA ESRL/PSD) def
 /version (2.0) def
 /history (created 2009/09 by Hoop (netCDF3)) def
 /Conventions (CF-1.2) def
 /title (4x Daily NOAA-CIRES 20th Century Reanalysis) def
 /comments (Data is from NOAA-CIRES 20th Century Reanalysis version 2 (4x/day).  It consists of most variables interpolated to pressure surfaces from model (sigma) surfaces.) def

grid:
/name (lon)def
/units (degree_east)def
 0.0 2. 358.
:grid

grid:
/name (lat)def
/units (degree_north)def
 90. 2. -90.
:grid

grid:
/name (time)def
/units (hours since 1800-1-1 00:00:0.0)def
values: 797688. :values
:grid

 /hgt {
[ lon lat | time ] (http://www.esrl.noaa.gov/psd/thredds/dodsC/Datasets/20thC_ReanV2/time_invariant/hgt.sfc.nc) readdatafile:
/name (hgt) def
 /level_desc (Surface) def
 /actual_range [ -523.90002 5685.2998 ] def
 /parent_stat (Other) def
 /add_offset 31266. def
 /long_name (Geopotential Height at Surface) def
 /precision 0 def
 /GRIB_id 7 def
 /valid_range [ -32766 28734 ] def
 /GRIB_name (HGT) def
 /var_desc (Geopotential height) def
 /Dataset (NOAA-CIRES 20th Century Reanalysis version 2) def
 /statistic (Ensemble Mean) def
 /missing_value 32766 def
 /standard_name (geopotential_height) def
 /unpacked_valid_range [ -1500. 60000. ] def
 /units /m def
 /shortarraytype opendaprecords :readdatafile
}defasvarsilent

:dataset

\end{ingrid}
