\begin{ingrid}
continuedataset:
grid:
/name (X)def
/units (degree_east)def
 0.5 1. 359.5
:grid
grid:
/name (Y)def
/units (degree_north)def
 -89.5 1. 89.5
:grid
grid:
/name (Z)def
/units (m)def
values: 0.0 10. 20. 30. 50. 75. 100. 125. 150. 200. 250. 300. 400. 500. 600. 700. 800. 900. 1000. 1100. 1200. 1300. 1400. 1500. 1750. 2000. 2500. 3000. 3500. 4000. 4500. 5000. 5500. :values
:grid
/basin {
%[ X Y | Z ] (/beluga/data/mbell/dldata/noaa.d/nodc.d/woa09.d/basin.msk)
[ X Y | Z ] (/Data/data8/noaa/nodc/WOA09/MASKS/basin.msk)
readdatafile:
       /name (basin) def
       /missing_value -100 def
       ((10F8.0)) formatted
       :readdatafile
       /long_name (basin code) def
toi1
/scale_min 1 def
/scale_max 58 def
/valid_min 1 def
/valid_max 58 def
/units /ids def
/CLIST[ 
(Atlantic Ocean)
(Pacific Ocean )
(Indian Ocean)
(Mediterranean Sea)
(Baltic Sea)
(Black Sea)
(Red Sea)
(Persian Gulf)
(Hudson Bay)
(Southern Ocean)
(Arctic Ocean)
(Sea of Japan)
(Kara Sea)
(Sulu Sea)
(Baffin Bay)
(East Mediterranean)
(West Mediterranean)
(Sea of Okhotsk)
(Banda Sea)
(Caribbean Sea)
(Andaman Basin)
(North Caribbean)
(Gulf of Mexico)
(Beaufort Sea)
(South China Sea)
(Barents Sea)
(Celebes Sea)
(Aleutian Basin)
(Fiji Basin)
(North American Basin)
(West European Basin)
(Southeast Indian Basin)
(Coral Sea)
(East Indian Basin)
(Central Indian Basin)
(Southwest Atlantic Basin)
(Southeast Atlantic Basin)
(Southeast Pacific Basin)
(Guatemala Basin)
(East Caroline Basin)
(Marianas Basin)
(Philippine Sea)
(Arabian Sea)
(Chile Basin)
(Somali Basin)
(Mascarene Basin)
(Crozet Basin)
(Guinea Basin)
(Brazil Basin)
(Argentine Basin)
(Tasman Sea)
(Atlantic Indian Basin)
(Caspian Sea)
(Sulu Sea II)
(Venezuela Basin)
(Bay of Bengal)
(Java Sea)
(East Indian Atlantic Basin)
] def
} defasvarsilent
\end{ingrid}
\begin{ingrid}
/mixnumber {
%[ X Y | Z ] (/beluga/data/mbell/dldata/noaa.d/nodc.d/woa09.d/mixnumber.msk)
[ X Y | Z ] (/Data/data8/noaa/nodc/WOA09/MASKS/mixnumber.msk)
readdatafile:
       /name (mixnumber) def
       /missing_value -100 def
       ((10F8.0)) formatted
       :readdatafile
       /long_name (mix number) def
       /valid_min -2 def
       /valid_max 2 def
toi4
} defasvarsilent
/landsea {
%[ X Y | ] (/beluga/data/mbell/dldata/noaa.d/nodc.d/woa09.d/landsea.msk)
[ X Y | ] (/Data/data8/noaa/nodc/WOA09/MASKS/landsea.msk)
readdatafile:
       /name (landsea) def
       /missing_value -100 def
       ((10F8.0)) formatted
       :readdatafile
       /long_name (landsea mask) def
/units (transition depth level) def
toi4
} defasvarsilent
:dataset
\end{ingrid}
