20 March 2006

Hi Benno,
Richard and I have a link from the North American Drought pages at Lamont to the Dai PDSI dataset

   http://iridl.ldeo.columbia.edu/expert/SOURCES/.NCAR/.CGD/.CAS/.Indices/.PDSI2004

which is currently password protected for just IRI access.  Richard has checked with Aiguo Dai
who has indicated that it may be distributed without restriction.  Would you be willing to add his link
and open up access to this dataset?
Thanks,
Naomi

p.s. the  new version of ingrid is working great on kage - the problem with the reanalysis monthly
data is gone.


---------- Forwarded message ----------
Date: Mon, 20 Mar 2006 12:59:50 -0700
From: Aiguo Dai <adai@ucar.edu>
To: Richard Seager <rich@maatkare.ldgo.columbia.edu>
Subject: Re: PDSI data set on Ingrid?

Richard,

It is ok to post it in the IRI/LDEO site. You might want to add a link to our website
(http://www.cgd.ucar.edu/cas/catalog/climind/pdsi.html) where we may post periodically (e.g., annually)
updated PDSI data.

I am doing fine. Hope everything is going well at Lamont.
Aiguo

Aiguo Dai, Scientist                         Email: adai@ucar.edu
Climate & Global Dynamics Division           Phone: 303-497-1357
National Center for Atmospheric Research     Fax  : 303-497-1333
P.O. Box 3000, Boulder, CO  80307, USA       www.cgd.ucar.edu/cas/adai/
Street Address: 1850 Table Mesa Drive, Boulder, CO 80305, USA



Richard Seager wrote:

>
> Hi Aiguo,
>
> We are wondering if you would mind if we placed your
> instrumental PDSI data set on our IRI/LDEO Ingrid-based
> data server:
>
> http://ingrid.ldgo.columbia.edu/
>
> in a way that would allow unrestricted access
> by all who use this data base (pretty much
> all climate researchers I think!).
>
> Currently the IRI maintain a version for use
> by IRI personnel omly that we at LDEO (and everyone
> else) cannot access.
>
> Hope all is well!
>
> Best,
> Richard
>

So we remove

/NotOpen dataareIRIonlyPassword
% Data set restricted at the request of the folks at CGD/CAS

\begin{ingrid}
continuedataset:
/description (Palmer Drought Severity Index (2004) from the National Center for Atmospheric Research) def
link:
/name /source def
/description (NCAR CAS PDSI page) def
/href (http://www.cgd.ucar.edu/cas/catalog/climind/pdsi.html) def
:link
grid: 
/name /X def
degE
periodic
-178.75 2.5 178.75
:grid
grid:
/name /Y def
degN
-58.75 2.5 76.25
:grid
grid:
/name /T def
/units (monthtime) def
16 Jan 1870 ensotime
1
16 Dec 2005 ensotime
:grid
variable:
/name /PDSI def
/long_name (Palmer Drought Severity Index) def
/missing_value -99999. def
/scale_min -15 def
/scale_max 15 def
grids: X Y | T :grids
file:
%/name (/beluga/data/mbell/pdsi.d/pdsi.monthly.maps.1870-2003.bin)def
%/name (/Data/data5/ucar/PDSI/pdsi.monthly.maps.1870-2003.bin) def
/name (/Data/data5/ucar/PDSI/pdsi.monthly.maps.1870-2005.fawc=1.r2.5x2.5) def
sequential
:file
:variable
variable:
/name /zindex def
/long_name (Z-Index) def
/missing_value -99999. def
%/scale_min -15 def
%/scale_max 15 def
grids: X Y | T :grids
file:
/name (/Data/data5/ucar/PDSI/zindex.monthly.maps.1870-2005.fawc=1.r2.5x2.5) def
sequential
:file
:variable
zindex
/UCAR_PDSI_ZINDEX datadownloadsareIRIonlyPassword
name exch def
grid:
/name /T def
/units (monthtime) def
16 Jan 1870 ensotime
1
16 Dec 2002 ensotime
:grid

variable:
/name (PDSIdT0) def
/missing_value -99999. def
/scale_min -15 def
/scale_max 15 def
grids: X Y | T :grids
file:
%/name (/beluga/data/mbell/pdsi.d/pdsi.monthly.maps.1870-2002.fawc.dT0) def
/name (/Data/data5/ucar/PDSI/pdsi.monthly.maps.1870-2002.fawc.dT0) def
sequential
:file
:variable
/references (Dai_etal2004) def
:dataset
%dup /PDSI.dataset_documentation.html get
% /dataset_documentation.html PDSI !
%/PDSI.dataset_documentation.html undef
\end{ingrid}
/reference (Dai, A., K. E. Trenberth, and T. Qian, 2004: A global data set of Palmer Drought Severity Index for 1870-2002: Relationship with soil moisture and effects of surface warming. J. Hydrometeorology, <b>5</b>, 1117-1130) def
