\begin{ingrid}
continuedataset:

/description (CRU TS3.22: Climatic Research Unit (CRU) Time-Series (TS) Version 3.22 of High Resolution Gridded Data of Month-by-month Variation in Climate (Jan. 1901 - Dec. 2013)) def

 /contact (BADC ) def
 /title (CRU TS3.22) def
 /comment (Data restrictions: for academic research use only.Contact BADC for details) def
 /Conventions (CF-1.4) def
 /references (Information on the data is available at http://badc.nerc.ac.uk/data/cru/) def
 /institution (Data held at British Atmospheric Data Centre, RAL, UK.) def
 /references (Harris_etal2014) def
 /note (CRU Conditions of Use states that acknowledgement should preferably be by citing one or more of the papers referenced) def

/citation (University of East Anglia Climatic Research Unit; Harris, I.; Jones, P.D. (2014): CRU TS3.22: Climatic Research Unit (CRU) Time-Series (TS) Version 3.22 of High Resolution Gridded Data of Month-by-month Variation in Climate (Jan. 1901- Dec. 2013). NCAS British Atmospheric Data Centre, 24 th September 2014. doi:10.5285/18BE23F8-D252-482D-8AF9-5D6A2D40990C. http://dx.doi.org/10.5285/18BE23F8-D252-482D-8AF9-5D6A2D40990C) def

link:
/name (BADC Documentation Page) def
/description (Climatic Research Unit (CRU) Time-Series (TS) Version 3.22 of High Resolution Gridded Data of Month-by-month Variation in Climate (Jan. 
1901 - Dec. 2013)) def
/href (http://catalogue.ceda.ac.uk/uuid/4a6d071383976a5fb24b5b42e28cf28f) def
:link

link:
/name (Reference Document) def
/description (Harris et al. (2014) International Journal of Climatology paper) def
/href (http://dx.doi.org/10.1002/joc.3711) def
:link


:dataset
\end{ingrid}
