\begin{ingrid}
continuedataset:
/IRIONLY datadownloadsareIRIonlyPassword
/long_name (Asian temperature from APHRODITE) def
/description (Asian temperature products created by the Research Institute for Humanity and Nature and Meteorological Research Institute of Japan Meteorological Agency) def
link: 
/name (APHRODITE's Water Resources Website) def
/href (http://aphrodite.st.hirosaki-u.ac.jp/) def
/description (the original source of this dataset) def
:link

/iridl:hasSemantics [(iridlsemantics:APHRODITE)(iridlsemantics:RIHN)(iridl:MRI)] def
/references (Kamiguchi2010 Kamiguchi2011 Yasutomi_etal2011 Yatagai_etal2012) def
:dataset
\end{ingrid}

Yasutomi, N., A. Hamada and A. Yatagai, 2011: Development of a 
       long-term daily gridded temperature dataset and its application to
       rain/snow discrimination of daily precipitation. Global Environmental
       Research, V15N2, pp165-172.

Yatagai, A., K. Kamiguchi, O. Arakawa, A. Hamada, N. Yasutomi and A. Kitoh (2012): APHRODITE:
Constructing a Long-term Daily Gridded Precipitation Dataset for Asia based on a Dense Network of
Rain Gauges, Bull. Amer. Meteor. Soc., 93, 1401-1415.
doi: http://dx.doi.org/10.1175/BAMS-D-11-00122.1

Kamiguchi, K., O. Arakawa, A. Kitoh, A. Yatagai, A. Hamada, and N. Yasutomi, 2010: Development of APHRO_JP, the first Japanese high-resolution daily precipitation product for more than 100 years, Hydrological Research Letters, 4, 60-64, doi:10.3178/HRL.4.60.

Kamiguchi, K., O. Arakawa, and A. Kitoh, 2011: Long-term Changes in Japanese Extreme Precipitation Analyzed with APHRO_JP_EX, Global Environmental Research, 15(2), 91-99.
