These data are in a variety of files, some netCDF, some direct access.
\begin{ingrid}
continuedataset:
/description (World Ocean Atlas 1994, an atlas of objectively analyzed fields of major ocean parameters at the annual, seasonal, and monthly time scales. Superceeded by WOA98) def
link:
/name (WOA98) def
/href (http://iridl.ldeo.columbia.edu/SOURCES/.NOAA/.NODC/.WOA98/) def
/description (World Ocean Atlas 1998 replaces LEVITUS94) def
/semantics /dcterm:isReplacedBy def
:link
/references (Conkright:etal1994 Levitus:Boyer1994a Levitus:etal1994 Levitus:Boyer1994c)def
/iridl:hasSemantics [(iridl:NOAA)(iridl:Ocean)] def
/name /LEVITUS94 cvx def
grid: /name /Z def
/long_name (Depth) def
/longname /Depth def
/units (m) def
/positive (down) def
[ 0.0 10. 20. 30. 50. 75. 100. 125. 150. 200. 250. 300. 400. 500. 600. 700. 800. 900. 1000. 1100. 1200. 1300. 1400. 1500. 1750. 2000. 2500. 3000. 3500. 4000. 4500. 5000. 5500.]
:grid
grid: /name (X) def
/long_name(Longitude) def
/units /degreeE def
periodic 
0.5 to 359.5 N= 360 pts
:grid
grid: /name (Y) def
/long_name(Latitude) def
/units /degreeN def
-89.5 to 89.5 N= 180 pts
:grid
grid: /name (T) def
/long_name (Time) def
periodic
month
Jan 1 Dec
:grid
/ANNUAL { /ANNUAL     (/Data/data1/lev94/lev94a.cdf) nameCDF
/rhoa
(/Data/data1/ocean/levitus94cache/rhoa.cdf) readCDF .rhoa
longname addhistory
/fullname [ /LEVITUS94 /ANNUAL /rhoa ] def
/long_name (density) def
/units (g/cm3 above 1) preferredunitname def
/dataset SOURCES .LEVITUS94 .ANNUAL def
  def
%/po4* {SOURCES .LEVITUS94 .ANNUAL .PO4 SOURCES .LEVITUS94 .ANNUAL .O2 43.5 mul 175 div add 1.95 sub 
%/name /po4* def
%/dataset SOURCES .LEVITUS94 .ANNUAL def
%/long_name ($@ PO sub 4 sup *$) def
%/fullname [ fullname aload pop pop long_name ] def
%} def
(/Data/data1/ocean/levitus94cache/po4s.cuf) continuewithCUF
/theta 
(/Data/data1/ocean/levitus94cache/theta.cdf) readCDF .$theta$
longname addhistory
/fullname [ /LEVITUS94 /ANNUAL /theta ] def
/long_name (potential temperature) def
/units /Celsius preferredunitname def
/dataset SOURCES .LEVITUS94 .ANNUAL def
/name /theta def
def
/temp temp /units /Celsius preferredunitname def 
def
dup {pop}{fullname type /stringtype eq {fullname interp /fullname exch def dataset name exch put}{pop}ifelse}foralldatasets2
/potdens {
theta sal 0 densa /long_name (potential density) def
} defasvar
dup /ANNUAL SOURCES .LEVITUS94  !
 } def
/SEASONAL { /SEASONAL (/Data/data1/lev94/lev94s.cdf) nameCDF 
/temp temp /units /Celsius preferredunitname def 
def
dup {pop}{fullname type /stringtype eq {fullname interp /fullname exch def dataset name exch put}{pop}ifelse}foralldatasets2
SOURCES .NOAA .NODC .WOA98 .SEASONAL .T
   name exch def
pushproc
  T replacewithdatasetGRID
popproc
/name /SEASONAL def
} defasvarsilent
/MONTHLY {/MONTHLY    (/Data/data1/lev94/lev94m.cdf) nameCDF
/theta
(/Data/data1/lev94/theta.cdf) readCDF .$theta$
/name /theta def
longname addhistory
/fullname [ /LEVITUS94 /MONTHLY /theta ] def
/dataset SOURCES .LEVITUS94 .MONTHLY def
def
%/Zmix
%(/Data/data1/lev94/zmix.cdf) readCDF .Z
%%/name /Zmix def
%/fullname [ /LEVITUS94 /MONTHLY /Zmix ] def
%/long_name (Mixed Layer Depth) def
%/dataset SOURCES .LEVITUS94 .MONTHLY def
%def
/potdens {
theta sal 0 densa /long_name (potential density) def
} defasvar
/Zmix {
potdens
   Z 0 VALUE
   1.2500002E-04 add
   potdens[Z]tablefunction
   potdens
    Z 0 VALUE
    1.2500002E-04 add
    SOURCES .LEVITUS94 .ANNUAL .potdens
     [Z]tablefunction
    replaceNaN
[X Y] REORDER
/long_name (mixed layer depth) def
} defasvarcache
/temp temp /units /Celsius preferredunitname def 
def
dup {pop}{fullname type /stringtype eq {fullname interp /fullname exch def dataset name exch put}{pop}ifelse}foralldatasets2
dup /MONTHLY SOURCES .LEVITUS94  !
 } def
:dataset
\end{ingrid}
\section{Zmix}
Zmix is computed from monthly data, except that a second version which
uses the ANNUAL mean data is used where the mixed-layer depth goes
below 1000 m.  The corresponding ingrid script follows
SOURCES .LEVITUS94 .MONTHLY
  a: .theta
    :a: .sal
     0 :a
    densa
  a:
    Z 0 VALUE
    1.2500002E-04 add
    :a: :a
   [Z]tablefunction
  SOURCES .LEVITUS94 .MONTHLY
   a: .theta
     :a: .sal
      0 :a
     densa
   Z 0 VALUE
   1.2500002E-04 add
   SOURCES .LEVITUS94 .ANNUAL
    a: .theta
      :a: .sal
       0 :a
      densa
    [Z]tablefunction
   replaceNaN

It is *very* slow, so until caching is automatic, it must be stored.

