\begin{ingrid}
continuedataset:

/description (CRU TS4.01: Climatic Research Unit (CRU) Time-Series (TS) Version 4.01 of High Resolution Gridded Data of Month-by-month Variation in Climate (Jan. 1901 - Dec. 2016)) def

 /contact (BADC) def
 /title (CRU TS4.01) def
 /comment (Access to these data is available to any registered CEDA user) def
 /Conventions (CF-1.4) def
 /references (Information on the data is available at http://badc.nerc.ac.uk/data/cru/) def
 /institution (Data held at British Atmospheric Data Centre, RAL, UK.) def
 /references (Harris_etal2020) def

 /note (CRU Conditions of Use states that acknowledgement should preferably be by citing one or more of the papers referenced) def

 /citation (University of East Anglia Climatic Research Unit; Harris, I.C.; Jones, P.D. (2017): CRU TS4.01: Climatic Research Unit (CRU) Time-Series (TS) version 4.01 of high-resolution gridded data o
f month-by-month variation in climate (Jan. 1901- Dec. 2016). Centre for Environmental Data Analysis, date of citation. http://catalogue.ceda.ac.uk/uuid/58a8802721c94c66ae45c3baa4d814d0) def

link:
/name (BADC Documentation Page) def
/description (Climatic Research Unit (CRU) Time-Series (TS) Version 4.01 of High Resolution Gridded Data of Month-by-month Variation in Climate (Jan. 1901 - Dec. 2016)) def
/href (http://catalogue.ceda.ac.uk/uuid/58a8802721c94c66ae45c3baa4d814d0) def
:link

link:
/name (Reference Document) def
/description (Harris et al. (2020) Scientific Data paper) def
/href (https://www.nature.com/articles/s41597-020-0453-3) def
:link

link:
/name (Release Notes) def
/description (Release notes for CRU TS v4.01: 15 September 2017) def
/href (https://crudata.uea.ac.uk/cru/data/hrg/cru_ts_4.01/Release_Notes_CRU_TS4.01.txt) def
:link

:dataset
\end{ingrid}
