\begin{ingrid}
continuedataset:

/description (CRU TS3.23: Climatic Research Unit (CRU) Time-Series (TS) Version 3.23 of High Resolution Gridded Data of Month-by-month Variation in Climate (Jan. 1901 - Dec. 2014)) def

 /contact (badc@rl.ac.uk) def
 /title (CRU TS3.23) def
 /comment (Access to these data is available to any registered CEDA user) def
 /Conventions (CF-1.4) def
 /references (Information on the data is available at http://badc.nerc.ac.uk/data/cru/) def
 /institution (Data held at British Atmospheric Data Centre, RAL, UK.) def
 /references (Harris_etal2014) def

 /note (CRU Conditions of Use states that acknowledgement should preferably be by citing one or more of the papers referenced) def

 /citation (University of East Anglia Climatic Research Unit; Harris, I.; Jones, P.D. (2015): CRU TS3.23: Climatic Research Unit (CRU) Time-Series (TS) Version 3.23 of High Resolution Gridded Data of Month-by-month Variation in Climate (Jan. 1901- Dec. 2014). Centre for Environmental Data Analysis, 09 November 2015. doi:10.5285/4c7fdfa6-f176-4c58-acee-683d5e9d2ed5. http://dx.doi.org/10.5285/4c7fdfa6-f176-4c58-acee-683d5e9d2ed5) def

link:
/name (BADC Documentation Page) def
/description (Climatic Research Unit (CRU) Time-Series (TS) Version 3.23 of High Resolution Gridded Data of Month-by-month Variation in Climate (Jan. 1901 - Dec. 2014)) def
/href (http://catalogue.ceda.ac.uk/uuid/5dca9487dc614711a3a933e44a933ad3) def
:link

link:
/name (Reference Document) def
/description (Harris et al. (2014) International Journal of Climatology paper) def
/href (http://dx.doi.org/10.1002/joc.3711) def
:link

:dataset
\end{ingrid}
