\begin{ingrid}
continuedataset:
link:
/name (GPCC_Home) def
/href (http://gpcc.dwd.de/) def
/description (GPCC Home Page) def
:link
link: 
/name (References) def
/href (http://www.dwd.de/bvbw/appmanager/bvbw/dwdwwwDesktop/?_nfpb=true&_pageLabel=_dwdwww_klima_umwelt_datenzentren_wzn&T12404518261141645246564gsbDocumentPath=Content%2FOeffentlichkeit%2FKU%2FKU4%2FKU42%2Fteaser__product__access.html&_state=maximized&_windowLabel=T12404518261141645246564&lastPageLabel=_dwdwww_klima_umwelt_datenzentren_wzn) def
:link
link:
/name (dataset_documentation) def
/href (http://www.dwd.de/bvbw/generator/DWDWWW/Content/Oeffentlichkeit/KU/KU4/KU42/en/Reports__Publications/GPCC__status__report__2010,templateId=raw,property=publicationFile.pdf/GPCC_status_report_2010.pdf) def
:link
link:
/name (GPCC_Products_2008) def
/href (ftp://ftp-anon.dwd.de/pub/data/gpcc/PDF/GPCC_intro_products_2008.pdf) def
:link
link:
/name (GPCC_Products_2011) def
/href (ftp://ftp-anon.dwd.de/pub/data/gpcc/PDF/GPCC_intro_products_v2011.pdf) def
:link
/long_name (Global Precipitation Climatology Centre) def
/iridl:hasSemantics (iridl:GPCC) def
/references (Rudolf_etal2010 Schneider_etal2008 Rudolf_Rubel2005 Rudolf_Schneider2005 Beck_etal2005 Rudolf_etal1994) def
:dataset
\end{ingrid}

Fuchs, T., U. Schneider and B. Rudolf (2007): Global Precipitation Analysis Products of the GPCC. Global Precipitation Climatology Centre (GPCC), DWD, Internet publication, 1-10.  (pdf 699 KB) http://www.dwd.de/en/FundE/Klima/KLIS/int/GPCC/Reports_Publications/QR/GPCC_intro_products_2007.pdf
#  
	Rudolf, B. & F. Rubel (2005): Global Precipitation. In: Hantel, M. (Ed.) Observed Global Climate. New Series on Landolt-Börnstein, Numerical Data and Functional Relationships, Springer, Berlin, 11.1 - 11.53, extended online version (11.1 - 11.24, print version). ISBN 3-540-20206-4. (pdf 7.200 KB) http://www.dwd.de/en/FundE/Klima/KLIS/int/GPCC/Reports_Publications/QR/LB_ObsGlobClim_ch11_Rudolf_Rubel.pdf
#  
	Rudolf, B., U. Schneider (2005): Calculation of Gridded Precipitation Data for the Global Land-Surface using in-situ Gauge Observations, Proceedings of the 2nd Workshop of the International Precipitation Working Group IPWG, Monterey October 2004, EUMETSAT, ISBN 92-9110-070-6, ISSN 1727-432X, 231-247. (pdf 522 KB)
http://www.dwd.de/en/FundE/Klima/KLIS/int/GPCC/Reports_Publications/QR/Rudolf-Calculation-IPWG-2005.pdf
#  
	Beck, C. , J. Grieser and B. Rudolf (2005): A New Monthly Precipitation Climatology for the Global Land Areas for the Period 1951 to 2000. DWD, Klimastatusbericht KSB 2004, ISSN 1437-7691, ISSN 1616-5063 (Internet), ISBN 3-88148-402-7, 181-190. (pdf 610 KB)
#  http://www.dwd.de/de/FundE/Klima/KLIS/prod/KSB/ksb04/28_precipitation.pdf

	Rudolf, B., H. Hauschild, W. Rueth and U. Schneider (1994): Terrestrial Precipitation Analysis: Operational Method and Required Density of Point Measurements. In: Global Precipitations and Climate Change (Ed. M. Desbois, F. Desalmond), NATO ASI Series I, Vol. 26, Springer-Verlag,
p. 173-186. (pdf 1.888 KB)
http://www.dwd.de/en/FundE/Klima/KLIS/int/GPCC/Reports_Publications/QR/Terrestrial.pdf
